Towards a standardized evaluation of multiple imputation routines

### 2022-03-22 Manuscript/StandardizedEvaluation.Rmd
recompile and save .tex

---
title: "Towards a standardized evaluation of multiple imputation routines"
author: "Hanne Oberman and Gerko Vink"
date: "19-1-2022"
abstract: "Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper we propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, we suggest a course of action for simulating and evaluating missing data problems."
bibliography: StandardizedEvaluation.bib  
output: pdf_document
editor_options: 
  chunk_output_type: inline
---

>>>>

---
title: "Towards a standardized evaluation of multiple imputation routines"
author: "Hanne Oberman and Gerko Vink"
date: "19-1-2022"
abstract: "Developing new imputation methodology has become a very active field. Unfortunately, there is no consensus on how to perform simulation studies to evaluate the properties of imputation methods. In this paper we propose a move towards a standardized evaluation of imputation methods. To demonstrate the need for standardization, we highlight a set of potential pitfalls that bring forth a chain of potential problems in the objective assessment of the performance of imputation routines. This may lead to suboptimal use of multiple imputation in practice. Additionally, we suggest a course of action for simulating and evaluating missing data problems."
bibliography: StandardizedEvaluation.bib  
output: 
  pdf_document:
    keep_tex: true
editor_options: 
  chunk_output_type: inline
---
